Simulation and Optimization of Injector Parameters with OpenFOAM and Globalizer Tools

### 2021-07-07 2021/ICNAAM/2021_ICNAAM.tex
final ICNAAM paper

The global optimization problem
\begin{eqnarray}\label{problem}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D\right\}},\\
&D=\left\{y\in R^N: a_j\leq y_j \leq b_j, 1\leq j \leq N \right\}.\label{D}
\end{eqnarray}

can serve as a mathematical model for the process of choosing optimum values of parameters $y=(y_1,y_2,...,y_N)$ of the engineering object under consideration.
The choice of the value  $y^*$ that determines the best option  is reduced to an approximate (with some required accuracy) solution of the above optimization problem based on the evaluation of object characteristics for the set of options $y^i\in D, \; 1 \leq i \leq k$, determined by available resources.

@@

At the same time. various dimensionality reduction schemes are widely used to reduce the complexity of designing global optimization algorithms. By means of  such schemes, it is possible to reduce solution of multidimensional optimization problems to the solution of one or more nested one-dimensional optimization problems.

@@

Step 3. Find the interval $(x_{t-1},x_t),$ with the maximum characteristic 
\[
R(t)=\max{R(i):1 \leq i \leq k}.
\]

@@

The fluid dynamics for the problem described in this paper is defined by the Navier-Stokes equations for an incompressible fluid:
\[
\nabla \cdot \vec{U} = 0,
\]
\[
\frac{\partial \vec{U}}{\partial t} + \nabla \cdot \left( \vec{U} \otimes \vec{U}\right) - \nabla \cdot v \left( \nabla \vec{U} + (\nabla \vec{U})^T\right) = - \frac{1}{\rho} \nabla p,
\]
where $\vec{U}$ is the velocity vector, $\nu$  is the liquid viscosity (assumed constant), $p$  is the overpressure, $\rho$ is the density of the liquid. In this system of equations, there are two unknown variables: $\vec{U}$  and $p$. For each of these variables, initial conditions are set: 
\[
\vec{U}(x,y) = 0,
\]
\[
p(x,y) = 0.
\]
There are three types of boundaries in the computational domain; special boundary conditions are set on each of them. 
On a rigid wall:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = 0.
\]
At the entrance to the computational domain:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = \vec{U_i}.
\]
At the exit of the computational domain:
\[
 p = 0,
\]
\[
\vec{U} = \vec{U_o}.
\]

>>>>

The global optimization problem
\begin{eqnarray}\label{problem}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D\right\}},\\
&D=\left\{y\in R^N: a_j\leq y_j \leq b_j, 1\leq j \leq N \right\},\label{D}
\end{eqnarray}
can serve as a mathematical model for the process of choosing optimum values of parameters $y=(y_1,y_2,...,y_N)$ of the engineering object under consideration.
The choice of the value  $y^*$ that determines the best option  is reduced to an approximate (with some required accuracy) solution of the above optimization problem based on the evaluation of object characteristics for the set of options $y^i\in D, \; 1 \leq i \leq k$, determined by available resources.

@@

At the same time, various dimensionality reduction schemes are widely used to reduce the complexity of designing global optimization algorithms. By means of  such schemes, it is possible to reduce solution of multidimensional optimization problems to the solution of one or more nested one-dimensional optimization problems.

@@

Step 3. Find the interval $(x_{t-1},x_t),$ with the maximum characteristic 
\[
R(t)=\max\{R(i):1 \leq i \leq k+1\}.
\]

@@

The fluid dynamics for the problem described in this paper is defined by the Navier-Stokes equations for an incompressible fluid:
\[
\nabla \cdot \vec{U} = 0,
\]
\[
\frac{\partial \vec{U}}{\partial t} + \nabla \cdot \left( \vec{U} \otimes \vec{U}\right) - \nabla \cdot \nu \left( \nabla \vec{U} + (\nabla \vec{U})^T\right) = - \frac{1}{\rho} \nabla p,
\]
where $\vec{U}$ is the velocity vector, $\nu$  is the liquid viscosity (assumed constant), $p$  is the overpressure, $\rho$ is the density of the liquid. In this system of equations, there are two unknown variables: $\vec{U}$  and $p$. For each of these variables, initial conditions are set: 
\[
\vec{U}(x,y) = 0,
\]
\[
p(x,y) = 0.
\]
There are three types of boundaries in the computational domain; special boundary conditions are set on each of them. 
On a rigid wall:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = 0.
\]
At the entrance to the computational domain:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = \vec{U_i}.
\]
At the exit of the computational domain:
\[
 p = 0,
\]
\[
\vec{U} = \vec{U_o}.
\]
